```{r echo=FALSE}
#Loading graphic library
library(ggplot2)
```
```{r loading, echo=FALSE}
#Loading dataset
ideas = read.csv("",header=TRUE,sep=",")
```
The effect of moderations in the Finland experiment
===================================================

Study on the effects of moderator interventions in the context of the crowdsourced policy-making processes conducted by the parliament of Finland.

Research Question
-----------------
How does moderation and peer-interaction impact the quantity of deliberation (argument exchange) in crowdsourced policy-making process?

### Study Objective
To compare the effects of moderator comments on the follow-up comments in idea's comment threads, i.e. made the threads in average longer than those in which the moderator didn't comment.

### Preliminar Analysis

#### Variables
We clustered the ideas generated during the traffic off-road policy making process in two groups. The first group, called **ideas moderated**, contains the ideas whose thread of comments have at least one comment from the moderator. The second group, called **ideas not moderated**, contains the ideas not intervened by the moderator.

**Explanatory variable:** whether the idea has or has not moderator comments

**Responsive variable:** number of participant comments generated in the idea

The following picture shows the difference between the number of comments generated in moderated ideas and the number of comments generated in not moderated ideas.

```{r boxplot, echo=FALSE, fig.width=6, fig.height=6}
ideas$moderated = ideas$moderator_comments>0
ideas$cond[ideas$moderated==TRUE] = "ideas moderated"
ideas$cond[ideas$moderated==FALSE] = "ideas not moderated"
ggplot(ideas, aes(x=ideas$cond, y=ideas$comments, fill=ideas$cond)) + 
      geom_boxplot() + guides(fill=FALSE) + 
      labs(x="", y="comments", title="Comments in ideas moderated vs comments in ideas not moderated") +
      theme(plot.title = element_text(size=12))
```

**Discussion**  
1. From the box plots we can be sure enough that each of the quantities represented in the picture, i.e. mean, first quartile, third quartile, are a little bit higher in the group of ideas moderated compared to the group of ideas not moderated. But just a little since the box plots overlap between them.  
2. In addition, by looking at the boxplot we can see that the spread of the data is quite different. In particular, the data in the group of ideas moderated are more spreaded than the data in the group of ideas not moderated, which are more concentrated.

Next let's continue our study by analyzing the following **summary** table
```{r summary, echo=FALSE, results='asis'}
#get only participant comments
comments_moderated = ideas[ideas$moderated==TRUE,3] - ideas[ideas$moderated==TRUE,4]
mean_moderated=mean(comments_moderated)
median_moderated=median(comments_moderated)
max_moderated=max(comments_moderated)
min_moderated=min(comments_moderated)
sd_moderated=sd(comments_moderated)
summary = matrix(c(length(comments_moderated),min_moderated,median_moderated,
                   mean_moderated,max_moderated,sd_moderated),ncol=6,byrow=TRUE)
comments_not_moderated = ideas[ideas$moderated==FALSE,3]
mean_not_moderated=mean(comments_not_moderated)
median_not_moderated=median(comments_not_moderated)
max_not_moderated=max(comments_not_moderated)
min_not_moderated=min(comments_not_moderated)
sd_not_moderated=sd(comments_not_moderated)
summary = rbind(summary,c(length(comments_not_moderated),min_not_moderated,
                                 median_not_moderated,mean_not_moderated,
                                 max_not_moderated,sd_not_moderated))
colnames(summary) = c('count','min','median','mean','max','SD')
rownames(summary) = c('ideas moderated','ideas not moderated')
print(xtable(summary, align=c('c','c','c', 'c', 'c', 'c', 'c')), type="html", comment=F, include.rownames=F)
#kable(summary,align=c('c','c','c','c','c','c'))
```
By looking at the table, it seems that the center of the data is quite higher in the group of ideas that had been moderated. Indeed, the numbers in the table illustrate that the **mean and median of comments in moderated ideas are fairly higher** than the **mean and median of comments in those ideas not moderated**. From this preliminar analysis we may say that the moderator interventions appear to influence the thread of comments, however, we can not be sure how significant it is.

### Formal Analysis
For finding out whether the influence we have seen is really significat or just something we may expect from the fluctuations of the data, we are going to conduct a more formal analysis. In particular, next will be performed a **hypothesis test**.  

#### Notations
  * *$\sf{mu_{m}}$*: mean of comments in the group of ideas moderated;
  * *$\sf{mu_{c}}$*: mean of comments in the group of ideas not moderated;
  * *$\alpha$*: level of significant.

#### Hypothesis
**$\sf{H_{0}}$:** *$\sf{mu_{m}}$ = $\sf{mu_{c}}$*, **$\sf{H_{A}}$:** *$\sf{mu_{m}}$ <> $\sf{mu_{c}}$*; *$\alpha$* = 0.05

#### Method
Since both groups contain different ideas this is a two-independent sample case. Having independent samples, we are going to apply the method *Welch-Satterthwaite Two Sample t-test with unequal variances* to study whether the data is consistent with the defined **$\sf{H_{0}}$**.

#### Result
The result obtained from applying the method to our two group of independent ideas is
```{r t-test, echo=FALSE}
test = t.test(comments_moderated, comments_not_moderated)
cat("P-value: ", test$p.value)
```

#### Discussion
1. Considering the extremely small value **p** obtained after applying the t-test, we reject our hyphotesis **$\sf{H_{0}}$** in favor of **$\sf{H_{A}}$**. Therefore, we can conclude that the **mean of comments** in moderated ideas **is not equal** to the mean of comments in those ideas in which the moderator has inteverned;
2. Looking at the 95% confidence interval we can also conclude that the **mean comments increases in a range of `r round(test$conf.int[1],3)` to `r round(test$conf.int[2],3)` in moderated ideas**.

#### Conclusion 
From this study, we can conclude that **moderation actions** within idea's comment threads **may impact positively** in the quantity of comments generated from the participants.
