---
title: "DQI Project - Coding Matching"
output: pdf_document
---

```{r, echo=FALSE}
calculate_coding_matching = function(type, data_coder1, data_coder2, data_coder3, cat_table, TOT_CATEGORIES,
                                     col_id, col_coder_name, MATCHING_THRESHOLD) {
  res_cod_tot = c()
  res_cod_f = c()
  matching_less_threshold = 0
  dis_cat_table = data.frame(cat_id=cat_table[,1],cat_name=cat_table[,2],dis_counter=rep(0,nrow(cat_table)))
  matching_less_threshold_per_idea = 0
  comments_counter = 0
  for (i in 1:nrow(data_coder1)) {
    coder = as.character(data_coder1[i,col_coder_name])
    row = c(coder,as.character(as.vector(data_coder1[i,col_id:ncol(data_coder1)])))
    res_cod_tot = rbind(res_cod_tot,row)
    coder = as.vector(data_coder2[i,col_coder_name])
    row = c(coder,as.character(as.vector(data_coder2[i,col_id:ncol(data_coder2)])))
    res_cod_tot = rbind(res_cod_tot,row)
    coder = as.vector(data_coder3[i,col_coder_name])
    row = c(coder,as.character(as.vector(data_coder3[i,col_id:ncol(data_coder3)])))
    res_cod_tot = rbind(res_cod_tot,row)
    res_cod_row = c()
    count_100 = 0
    dis_cat = ''
    dis_cat_counter = 0
    comments_counter = comments_counter + 1
    for (j in 3:ncol(data_coder1)) {
      coder1_cod = as.character(data_coder1[i,j])
      coder2_cod = as.character(data_coder2[i,j])
      coder3_cod = as.character(data_coder3[i,j])
      cat_id = as.numeric(cat_table[cat_table[,2]==colnames(data_coder1)[j],1])
      if (is.na(coder1_cod)) {
        coder1_cod = 'NA'
      }
      if (is.na(coder2_cod)) {
        coder2_cod = 'NA'
      }
      if (is.na(coder3_cod)) {
        coder3_cod = 'NA'
      }
      if (coder1_cod == coder2_cod && coder1_cod == coder3_cod && coder2_cod == coder3_cod) {
        res_cod = 100
        count_100 = count_100 + 1
      } else {
        if (coder1_cod != coder2_cod && coder1_cod != coder3_cod && coder2_cod != coder3_cod) {
          res_cod = 0
        } else {
          res_cod = 50
        }
        dis_cat = paste(dis_cat, cat_id, " ", sep="")  
        dis_cat_counter = dis_cat_counter + 1
        dis_cat_table[dis_cat_table$cat_id==cat_id,"dis_counter"] = 
          dis_cat_table[dis_cat_table$cat_id==cat_id,"dis_counter"] + 1
      }
      res_cod_row = cbind(res_cod_row, res_cod)
    }
    matching = round(((count_100/TOT_CATEGORIES)*100),0)
    res_cod_row = cbind(matching,res_cod_row)
    res_cod_row = cbind('Matching',res_cod_row)
    res_cod_tot = rbind(res_cod_tot,res_cod_row)
    colnames(res_cod_row) = colnames(data_coder1)
    if (matching < MATCHING_THRESHOLD) {
      res_cod_f = rbind(res_cod_f, c(paste('**',data_coder1[i,col_id],'**',sep=''),
                                     matching,dis_cat_counter,dis_cat))
      matching_less_threshold = matching_less_threshold + 1
      matching_less_threshold_per_idea = matching_less_threshold_per_idea + 1
    } 
    else {
      res_cod_f = rbind(res_cod_f, c(data_coder1[i,col_id],matching,dis_cat_counter,dis_cat))  
    }
    if (type == 'comments') {
      current_idea_id = as.numeric(strsplit(data_coder1[i,col_id],'_')[[1]][1])
      if (i < nrow(data_coder1)) {
        next_idea_id = as.numeric(strsplit(data_coder1[i+1,col_id],'_')[[1]][1])
      }
      else {
        next_idea_id = -10000
      }
      if (current_idea_id != next_idea_id) {
        comments_dis = round((matching_less_threshold_per_idea/comments_counter)*100,0)
        msg = paste(matching_less_threshold_per_idea,' (', comments_dis ,'%)  comm. cod. match. < ', 
                    MATCHING_THRESHOLD, '%', sep='')
        res_cod_f = rbind(res_cod_f, c(msg,'','',''))
        matching_less_threshold_per_idea = 0
        comments_counter = 0
      }
    }
  } 
  colnames(res_cod_tot) = colnames(data_coder1)
  
  ret = list(full_table=res_cod_tot,summary_table=res_cod_f,dis_cat_table=dis_cat_table,
             tot_less_threshold=matching_less_threshold)
  
  return(ret)
}
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Load libraries
library(dplyr)
library(knitr)
```

```{r, echo=FALSE}
# Set constant
TOT_CATEGORIES = 36
MATCHING_THRESHOLD = 80
FIRST_CATEGORY_COLUMN = 9
```

```{r, echo=FALSE}
# load column name
col_names = read.table("./data/dqi_analysis_columns.txt", sep=" ")
# load reports
tanja = read.csv("./data/tanja_dqi_2.csv", header=T, sep=",", stringsAsFactor=F)
tanja = tanja[,1:nrow(col_names)]
aurin = read.csv("./data/aurin_dqi_3.csv", header=T, sep=",", stringsAsFactor=F)
aurin = aurin[,1:nrow(col_names)]
jukan = read.csv("./data/jukan_dqi_3.csv", header=T, sep=",", stringsAsFactor=F)
jukan = jukan[,1:nrow(col_names)]
# pre-process datasets
colnames(tanja) = col_names[,2]
colnames(aurin) = col_names[,2]
colnames(jukan) = col_names[,2]
coder_tanja = list(Coder=rep('tanja',nrow(tanja)))
coder_aurin = list(Coder=rep('aurin',nrow(aurin)))
coder_jukan = list(Coder=rep('jukan',nrow(jukan)))
tanja = cbind(coder_tanja, tanja)
aurin = cbind(coder_aurin, aurin)
jukan = cbind(coder_jukan, jukan)
```

## Categories

```{r, echo=FALSE}
cat_table = c()
c = 1
for (idx in FIRST_CATEGORY_COLUMN:nrow(col_names)) {
  cat_table = rbind(cat_table, c(c, as.character(col_names[idx,2])))
  cat(paste('(', c, ') ' , col_names[idx,2], '\n', sep=""))
  c = c + 1
}
colnames(cat_table) = c('Cat_Id','Cat_Name')
```

# Ideas Coding Matching

```{r, echo=FALSE, results='markup'}
# analysis idea coding reliability
tanja_i = tanja %>% select(Coder, Idea_Id, (FIRST_CATEGORY_COLUMN+1):nrow(col_names)) %>% filter(!is.na(Idea_Id))
aurin_i = aurin %>% select(Coder, Idea_Id, (FIRST_CATEGORY_COLUMN+1):nrow(col_names)) %>% filter(!is.na(Idea_Id))
jukan_i = jukan %>% select(Coder, Idea_Id, (FIRST_CATEGORY_COLUMN+1):nrow(col_names)) %>% filter(!is.na(Idea_Id)) 
tot_ideas = nrow(tanja_i)
ret = calculate_coding_matching('ideas', tanja_i,aurin_i,jukan_i,cat_table,TOT_CATEGORIES,
                                2,1,MATCHING_THRESHOLD)
table = data.frame(idea_id=ret$summary_table[,1],matching_per=ret$summary_table[,2],
                   num_dis_cat=ret$summary_table[,3], dis_cat=ret$summary_table[,4])
colnames(table) = c('Idea Id','Matching %','# Conflict Cats.', '(Id) Conflict Cats.')
kable(table, format = "pandoc", align=c('c','c','c'), row.names=F)
```

*Obs.* In **bold** ideas with less than `r MATCHING_THRESHOLD`% of coding matching

**Out of the `r tot_ideas` ideas, `r ret$tot_less_threshold` (`r round((ret$tot_less_threshold/tot_ideas)*100,0)`%) have coding matching below `r MATCHING_THRESHOLD`%.**

### Least Matching Categories

```{r echo=FALSE}
dis_cat_table = ret$dis_cat_table %>% filter(dis_counter>0) %>% 
                  arrange(desc(dis_counter)) %>% select(cat_name:dis_counter)
colnames(dis_cat_table) = c('Cat. Name', paste('# Ideas in conflict (Out of ', tot_ideas, ')', sep=''))
kable(dis_cat_table, format = "pandoc", align=c('c','c'), row.names=F)
```


# Comments Coding Matching

```{r, echo=FALSE, results='markup'}
for (idx in 1: nrow(tanja)) {
  if (!is.na(tanja[idx,"Idea_Id"])) {
    idea_id = tanja[idx,"Idea_Id"]
  }
  tanja[idx,"Comment_Num"] = paste(idea_id, '_', tanja[idx,"Comment_Num"], sep='')
  aurin[idx,"Comment_Num"] = paste(idea_id, '_', aurin[idx,"Comment_Num"], sep='')
  jukan[idx,"Comment_Num"] = paste(idea_id, '_', jukan[idx,"Comment_Num"], sep='')
}
tanja_c = tanja %>% filter(is.na(Idea_Id)) %>% select(-(Idea_Id:Comment)) %>% rename(Comment_Id=Comment_Num)
aurin_c = aurin %>% filter(is.na(Idea_Id)) %>% select(-(Idea_Id:Comment)) %>% rename(Comment_Id=Comment_Num) 
jukan_c = jukan %>% filter(is.na(Idea_Id)) %>% select(-(Idea_Id:Comment)) %>% rename(Comment_Id=Comment_Num)
tot_comments = nrow(tanja_c)
ret = calculate_coding_matching('comments', tanja_c,aurin_c,jukan_c,cat_table,TOT_CATEGORIES,
                                2,1,MATCHING_THRESHOLD)
table = data.frame(idea_id=ret$summary_table[,1],matching_per=ret$summary_table[,2],
                   num_dis_cat=ret$summary_table[,3], dis_cat=ret$summary_table[,4])
colnames(table) = c('Comment Id (Idea_Id+#Comment)','Matching %','# Conflict Cats.', '(Id) Conflict Cats.')
kable(table, format = "pandoc", align=c('c','c','c'), row.names=F)
```

*Obs.* In **bold** comments with less than `r MATCHING_THRESHOLD`% of coding matching

**Out of the `r tot_comments` comments, `r ret$tot_less_threshold` (`r round((ret$tot_less_threshold/tot_comments)*100,0)`%) have coding matching below `r MATCHING_THRESHOLD`%.**

### Least Matching Categories

```{r echo=FALSE}
dis_cat_table = ret$dis_cat_table %>% filter(dis_counter>0) %>% 
                  arrange(desc(dis_counter)) %>% select(cat_name:dis_counter)
colnames(dis_cat_table) = c('Cat. Name', paste('# Comments in conflict (Out of ', tot_comments, ')', sep=''))
kable(dis_cat_table, format = "pandoc", align=c('c','c'), row.names=F)
```