---
output: html_document
---
```{r echo=FALSE}
#Loading graphic library
library(ggplot2)
library(xtable)
```
```{r loading, echo=FALSE}
#Loading dataset
users = read.csv("",header=TRUE,sep=";",stringsAsFactors=FALSE)
total_reg = nrow(users)
```

Participation in the Finland experiment
======================================

Study on the dynamics of participation detected in the Finland crowdsourced law-reform process conducted in the idea management system [IdeaScale](http://www.ideascale.com).

### Data Snippet
The data set contains information of **`r total_reg`** users.

```{r echo=FALSE, results='asis'}
print(xtable(head(users[50:55,c("id","ideas","votes","comments")]),
             align=c('c','c','c','c','c')), type="html", comment=F, include.rownames=FALSE)
```

### Ideas
How the production of ideas is distributed throughout the set of users.

*Distribution (without outliers)*

```{r ideas_dist, echo=FALSE, fig.width=6, fig.height=6}
producers = users[users$ideas>0 & users$ideas<=20,] # Get rid of users that didn't produce ideas
ggplot(producers, aes(x=ideas)) + 
  geom_histogram(binwidth=0.5) +
  #geom_vline(xintercept = mean_producers, linetype = 'dashed', color = 'red', size = 1) +
  scale_x_continuous(breaks=c(0:20)) +
  labs(x="Num. Ideas Posted", y="Users Count")
```

```{r ideas_tot, echo=FALSE}
tot_ideas = sum(users$ideas)
total_ideators = length(users[users$ideas>0,"ideas"])
per_ideators = paste(round(total_ideators / total_reg * 100,2),"%",sep="")
cat("Total Ideas: ",tot_ideas,"\nTotal Ideators: ",total_ideators," (",per_ideators," of participants )")
```

*Five-number summary*
```{r ideas_sum, echo=FALSE}
summary(users$ideas)
```

*Trimmed Mean*
```{r, echo=FALSE}
#sortedIdeas = sort(users$ideas)
#trimmedMean = mean(sortedIdeas, trim=0.005)
cat("Mean without the outliers (> 20 ideas posted): ",round(mean(users[users$ideas<=20,"ideas"]),3))
```

*Top Ten Ideators*
```{r, echo=FALSE, results='asis'}
order = order(users$ideas,decreasing=TRUE)
users_idea_producers = users[order,]
users_idea_producers["percentage of total"] = paste(round(users_idea_producers$ideas / tot_ideas * 100,1),"%")
top_10_ideators = users_idea_producers[1:10,c("id","ideas","percentage of total")]
print(xtable(top_10_ideators, align=c('c','c','c','c')), type="html", comment=F, include.rownames=FALSE)
```
```{r, echo=FALSE}
cat("They produce: ", round((sum(top_10_ideators$ideas)*100/tot_ideas),2), "% of the ideas.")
```

*Distribution of ideators by the number of ideas posted*
```{r, echo=FALSE, results='asis'}
#Counting 1 to 5 idea producers
count_users_1_idea = length(users[users$ideas==1,"ideas"])
per_users_1_idea = paste(round(count_users_1_idea / total_reg * 100,2),"%")
count_users_2_idea = length(users[users$ideas==2,"ideas"])
per_users_2_idea = paste(round(count_users_2_idea / total_reg * 100,2),"%")
count_users_3_idea = length(users[users$ideas==3,"ideas"])
per_users_3_idea = paste(round(count_users_3_idea / total_reg * 100,2),"%")
count_users_4_idea = length(users[users$ideas==4,"ideas"])
per_users_4_idea = paste(round(count_users_4_idea / total_reg * 100,2),"%")
count_users_5_idea = length(users[users$ideas==5,"ideas"])
per_users_5_idea = paste(round(count_users_5_idea / total_reg * 100,2),"%")
#Counting 6 to 10 idea producers
users_6_10 = length(users[users$ideas>5&users$ideas<=10,"ideas"])
per_users_6_10 = paste(round(users_6_10 / total_reg * 100,2),"%")
#Counting 11 to 15 idea producers
users_11_15 = length(users[users$ideas>10&users$ideas<=15,"ideas"])
per_users_11_15 = paste(round(users_11_15 / total_reg * 100,2),"%")
#Counting >15 idea producers
users_16 = length(users[users$ideas>15,"ideas"])
per_users_16 = paste(round(users_16 / total_reg * 100,2),"%")
#Counting total idea producers
total_producers = count_users_1_idea + count_users_2_idea + count_users_3_idea +     count_users_4_idea + count_users_5_idea + users_6_10 + users_11_15 + users_16
per_total_prod = paste(round(total_producers / total_reg * 100,2),"%")
#Creating matrix of idea producers
idea_producers = matrix(c(count_users_1_idea,count_users_2_idea,count_users_3_idea,
                           count_users_4_idea,count_users_5_idea,users_6_10,
                           users_11_15,users_16,total_producers),ncol=9,byrow=TRUE)
idea_producers = rbind(idea_producers,c(per_users_1_idea,per_users_2_idea,
                                          per_users_3_idea,per_users_4_idea,
                                          per_users_5_idea,per_users_6_10,
                                          per_users_11_15,per_users_16,per_total_prod))
colnames(idea_producers) = c("1 idea","2 ideas","3 ideas","4 ideas","5 ideas",
                              "6-10 ideas","10-15 ideas",">15 ideas",
                              "Total Idea producers")
rownames(idea_producers) = c("Count","Percentage")
print(xtable(idea_producers, align=c('c','c','c','c','c','c','c','c','c','c')), type="html", comment=F, include.rownames=T)
```

### Votes
How voting is distributed throughout the set of users.

*Distribution*

```{r votes_dist, echo=FALSE, fig.width=6, fig.height=6}
qplot(users$votes, data=users, geom="histogram", xlab="Votes", binwidth=10) +
geom_vline(xintercept = mean(users$votes), linetype = 'dashed', color = 'red', size = 1)
```

**obs.** The mean of the distribution is depicted by the red line

```{r votes_tot, echo=FALSE}
tot_votes = sum(users$votes)
total_voters = length(users[users$votes>0,"votes"])
per_voters = paste(round(total_voters / total_reg * 100,2),"%",sep="")
cat("Total Votes: ",tot_votes,"\nTotal Voters: ",total_voters," (",per_voters," of participants )")
```

*Five-number summary*
```{r votes_sum, echo=FALSE}
summary(users$votes)
```

*Trimmed Mean*
```{r, echo=FALSE}
cat("Mean without the outliers (>300 votes): ",round(mean(users[users$votes<=300,"votes"]),3))
```

*Top Ten Voters*
```{r, echo=FALSE, results='asis'}
order = order(users$votes,decreasing=TRUE)
users_voters = users[order,]
users_voters["percentage of total"] = paste(round(users_voters$votes/tot_votes * 100,1),"%")
top_10_voters = users_voters[1:10,c("id","votes","percentage of total")]
print(xtable(top_10_voters, align=c('c','c','c', 'c')), type="html", comment=F, include.rownames=F)
#kable(top_10_voters,format="markdown",row.names=FALSE,align=c('c','c','c','c'))
```

*Distribution of voters by the number of votes posted*
```{r, echo=FALSE, results='asis'}
#Creating matrix of voters
voters_1_10 = length(users[users$votes>0&users$votes<=10,"votes"])
voters_10_20 = length(users[users$votes>10&users$votes<=20,"votes"])
voters_20_30 = length(users[users$votes>20&users$votes<=30,"votes"])
voters_30_40 = length(users[users$votes>30&users$votes<=40,"votes"])
voters_40_50 = length(users[users$votes>40&users$votes<=50,"votes"])
voters_50_100 = length(users[users$votes>50&users$votes<=100,"votes"])
voters_100_200 = length(users[users$votes>100&users$votes<=200,"votes"])
voters_200_300 = length(users[users$votes>200&users$votes<=300,"votes"])
voters_300 = length(users[users$votes>300,"votes"])
voters = matrix(c(voters_1_10,voters_10_20,voters_20_30,voters_30_40,
                  voters_40_50,voters_50_100,voters_100_200,voters_200_300,
                  voters_300,total_voters),ncol=10,byrow=TRUE)
voters = rbind(voters,c(paste(round(voters_1_10 / total_reg * 100,2),"%"),
                        paste(round(voters_10_20 / total_reg * 100,2),"%"),
                        paste(round(voters_20_30 / total_reg * 100,2),"%"),
                        paste(round(voters_30_40 / total_reg * 100,2),"%"),
                        paste(round(voters_40_50 / total_reg * 100,2),"%"),
                        paste(round(voters_50_100 / total_reg * 100,2),"%"),
                        paste(round(voters_100_200 / total_reg * 100,2),"%"),
                        paste(round(voters_200_300 / total_reg * 100,2),"%"),
                        paste(round(voters_300 / total_reg * 100,2),"%"),
                        per_voters))
colnames(voters) = c("1-10 votes","11-20 votes","21-30 votes","31-40 votes","41-50 votes","51-100 votes","101-200 votes","201-300 votes",">300","Total Voters")
rownames(voters) = c("Count","Percentage")
print(xtable(voters, align=c('c','c','c','c','c','c','c','c','c','c', 'c')), type="html", comment=F, include.rownames=T)
#kable(voters,align=c('c','c','c','c','c','c','c','c','c','c'))
```

### Comments
How commenting activities are distributed throughout the set of users.

*Distribution*

```{r comments_dist, echo=FALSE, fig.width=6, fig.height=6}
qplot(users$comments, data=users, geom="histogram", xlab="Comments", binwidth=10) +
geom_vline(xintercept = mean(users$comments), linetype = 'dashed', color = 'red', size = 1)
```

**obs.** The read line depicts the mean of the distribution

```{r comments_tot, echo=FALSE}
tot_comments = sum(users$comments)
total_commenters = length(users[users$comments>0,"comments"])
per_commenters = paste(round(total_commenters / total_reg * 100,2),"%",sep="")
cat("Total Comments: ",tot_comments,"\nTotal Commenters: ",total_commenters," (",per_commenters," of participants )")
```

*Five-number summary*
```{r comments_sum, echo=FALSE}
summary(users$comments)
```

*Trimmed Mean*
```{r, echo=FALSE}
cat("Mean without the outliers (>100 comments): ",round(mean(users[users$comments<=100,"comments"]),3))
```

*Top Ten Commenters*
```{r, echo=FALSE, results='asis'}
order = order(users$comments,decreasing=TRUE)
user_commenters = users[order,]
user_commenters["percentage of total"] = paste(round(user_commenters$comments/tot_comments * 100,1),"%")
top_10_commenters = user_commenters[1:10,
                                     c("id","comments","percentage of total")]
print(xtable(top_10_commenters, align=c('c','c','c', 'c')), type="html", comment=F, include.rownames=F)
#kable(top_10_commenters,format="markdown",row.names=FALSE,align=c('c','c','c','c'))
```

*Distribution of commenters by the number of comments posted*
```{r, echo=FALSE, results='asis'}
commenters_1_5 = length(users[users$comments>0&users$comments<=5,"comments"])
commenters_5_10 = length(users[users$comments>5&users$comments<=10,"comments"])
commenters_10_20 = length(users[users$comments>10&users$comments<=20,"comments"])
commenters_20_30 = length(users[users$comments>20&users$comments<=30,"comments"])
commenters_30_40 = length(users[users$comments>30&users$comments<=40,"comments"])
commenters_40_50 = length(users[users$comments>40&users$comments<=50,"comments"])
commenters_50 = length(users[users$comments>50,"comments"])
commenters = matrix(c(commenters_1_5,commenters_5_10,commenters_10_20,
                      commenters_20_30,commenters_30_40,commenters_40_50,
                      commenters_50,total_commenters),
                      ncol=8,byrow=TRUE)
commenters = rbind(commenters,c(paste(round(commenters_1_5 / total_reg * 100,2),"%"),
                        paste(round(commenters_5_10 / total_reg * 100,2),"%"),
                        paste(round(commenters_10_20 / total_reg * 100,2),"%"),
                        paste(round(commenters_20_30 / total_reg * 100,2),"%"),
                        paste(round(commenters_30_40 / total_reg * 100,2),"%"),
                        paste(round(commenters_40_50 / total_reg * 100,2),"%"),
                        paste(round(commenters_50 / total_reg * 100,2),"%"),
                        per_commenters))
colnames(commenters) = c("1-5 comments","6-10 comments","11-20 comments",
                         "21-30 comments","31-40 comments",
                         "41-50 comments","> 50 comments","Tot Comm.")
rownames(commenters) = c("Count","Percentage")
print(xtable(commenters, align=c('c','c','c','c','c','c','c','c','c')), type="html", comment=F, include.rownames=T)
#kable(commenters,align=c('c','c','c','c','c','c','c','c'))
```

### Discussion
The following table summarizes the **participation of the registered users**, for example, it shows, in the second row, that half of the users (374) participated only by voting on the existing ideas, or that 12.6% (94) of the users did not make any contribution.

```{r, echo=FALSE, results='asis'}
#Getting the number of users that did not produce any content (ideas, votes, comments)
inactive_users = length(users[users$ideas==0&users$votes==0&users$comments==0,"id"])
per_inactive = paste(round(inactive_users / total_reg * 100,2),"%")

#Getting the number of users that posted ideas but not comments nor votes
users_only_ideas = length(users[users$ideas>0&users$votes==0&users$comments==0,"id"])
per_only_ideas = paste(round(users_only_ideas / total_reg * 100,2),"%")

#Getting the number of users that voted but did not comment nor post ideas
users_only_votes = length(users[users$ideas==0&users$votes>0&users$comments==0,"id"])
per_only_votes = paste(round(users_only_votes / total_reg * 100,2),"%")

#Getting the number of users that commented but did not post ideas nor voted
users_only_comments = length(users[users$ideas==0&users$votes==0&users$comments>0,"id"])
per_only_comments = paste(round(users_only_comments / total_reg * 100,2),"%")

#Getting the number of users that posted ideas and votes but not comments
users_ideas_votes = length(users[users$ideas>0&users$votes>0&users$comments==0,"id"])
per_ideas_votes = paste(round(users_ideas_votes / total_reg * 100,2),"%")

#Getting the number of users that posted ideas and comments but not votes
users_ideas_comments = length(users[users$ideas>0&users$votes==0&users$comments>0,"id"])
per_ideas_comments = paste(round(users_ideas_comments / total_reg * 100,2),"%")

#Getting the number of users that posted comments and votes but not ideas
users_votes_comments = length(users[users$ideas==0&users$votes>0&users$comments>0,"id"])
per_votes_comments = paste(round(users_votes_comments / total_reg * 100,2),"%")

#Getting the number of users that posted ideas, comments and votes
users_ideas_votes_comments = length(users[users$ideas>0&users$votes>0&users$comments>0,"id"])
per_ideas_votes_comments = paste(round(users_ideas_votes_comments / total_reg * 100,2),"%")

#Creating the summary table
summary_mat = matrix(c(users_only_ideas,per_only_ideas,'X','',''),ncol=5,byrow=TRUE)
summary_mat = rbind(summary_mat,c(users_only_votes,per_only_votes,'','X',''))
summary_mat = rbind(summary_mat,c(users_only_comments,per_only_comments,'','','X'))
summary_mat = rbind(summary_mat,c(users_ideas_votes,per_ideas_votes,'X','X',''))
summary_mat = rbind(summary_mat,c(users_ideas_comments,per_ideas_comments,'X','','X'))
summary_mat = rbind(summary_mat,c(users_votes_comments,per_votes_comments,'','X','X'))
summary_mat = rbind(summary_mat,c(users_ideas_votes_comments,per_ideas_votes_comments,'X','X','X'))
summary_mat = rbind(summary_mat,c(inactive_users,per_inactive,'','',''))
colnames(summary_mat) = c('number of users','% of total users','ideating','voting','commenting')

print(xtable(summary_mat, align=c('c','c','c','c','c','c')), type="html", comment=F, include.rownames=F)
#kable(summary_mat,align=c('c','c','c','c','c'))
```

Next, it is presented the list of users that were top-ranked in all the three lists presented above. They are the **most active** users being in the rank of the 10 users that most posted ideas, comments and votes.
```{r, echo=FALSE, results='asis'}
#Get a list of the top-ten ideators, voters and commenters (intersection of the three sets)
top_10 = Reduce(intersect, list(top_10_ideators$id,top_10_voters$id,
                                top_10_commenters$id))
remove(top_10_m)
for (id in top_10) {
  if (exists("top_10_m")) {
    top_10_m = rbind(top_10_m,c(as.character(top_10_ideators[top_10_ideators$id==id,
                                                         "id"]),
                    paste(top_10_ideators[top_10_ideators$id==id,"ideas"]," (",
                          top_10_ideators[top_10_ideators$id==id,
                                          "percentage of total"]," of total)", sep=""),
                    paste(top_10_voters[top_10_voters$id==id,"votes"]," (",   
                          top_10_voters[top_10_voters$id==id,
                                        "percentage of total"]," of total)", sep=""),
                    paste(top_10_commenters[top_10_commenters$id==id,"comments"],
                          " (",top_10_commenters[top_10_commenters$id==id,
                                                "percentage of total"]," of total)", sep="")))
  } else {
    top_10_m = matrix(c(as.character(top_10_ideators[top_10_ideators$id==id,
                                                     "id"]),
                    paste(top_10_ideators[top_10_ideators$id==id,"ideas"]," (",
                          top_10_ideators[top_10_ideators$id==id,
                                          "percentage of total"]," of total)", sep=""),
                    paste(top_10_voters[top_10_voters$id==id,"votes"]," (",   
                          top_10_voters[top_10_voters$id==id,
                                        "percentage of total"]," of total)", sep=""),
                    paste(top_10_commenters[top_10_commenters$id==id,"comments"],
                          " (",top_10_commenters[top_10_commenters$id==id,
                                                "percentage of total"]," of total)", sep="")),
                  ncol=4,byrow=TRUE)    
  } 
}
colnames(top_10_m) = c("id","ideas","votes","comments")
print(xtable(top_10_m, align=c('c','c','c','c','c')), type="html", comment=F, include.rownames=F)
#kable(top_10_m,align=c('c','c','c','c'))
```

The following table summarizes the list of users that were top-10-ranked among the users that most ideas and comments posted.
```{r, echo=FALSE, results='asis'}
#Get who are at the top-ten lists of ideators and commenters (intersection of two sets)
top_10_ideas_comments = Reduce(intersect, list(top_10_ideators$id,
                                               top_10_commenters$id))
remove(top_10_m_ic)
for (id in top_10_ideas_comments) {
  if (exists("top_10_m_ic")) {
    top_10_m_ic = rbind(top_10_m_ic,c(as.character(top_10_ideators[top_10_ideators$id==id
                                                                   ,"id"]),
                    paste(top_10_ideators[top_10_ideators$id==id,"ideas"]," (",
                          top_10_ideators[top_10_ideators$id==id,
                                          "percentage of total"]," of total)", sep=""),
                    paste(top_10_commenters[top_10_commenters$id==id,"comments"],
                          " (",top_10_commenters[top_10_commenters$id==id,
                                                "percentage of total"]," of total)", sep="")))
  } else {
    top_10_m_ic = matrix(c(as.character(top_10_ideators[top_10_ideators$id==id,"id"]),
                    paste(top_10_ideators[top_10_ideators$id==id,"ideas"]," (",
                          top_10_ideators[top_10_ideators$id==id,
                                          "percentage of total"]," of total)", sep=""),
                    paste(top_10_commenters[top_10_commenters$id==id,"comments"],
                          " (",top_10_commenters[top_10_commenters$id==id,
                                                "percentage of total"]," of total)", sep="")),
                  ncol=3,byrow=TRUE)      
  }
}
colnames(top_10_m_ic) = c("id","ideas","comments")
print(xtable(top_10_m_ic, align=c('c','c','c','c')), type="html", comment=F, include.rownames=F)
#kable(top_10_m_ic,align=c('c','c','c'))
```

Next, it is outlined the list of users top-10-ranked as the users that most comments and votes placed.
```{r, echo=FALSE, results='asis'}
#Get who are at the top-ten lists of ideators and voters (intersection of two sets)
top_10_ideas_votes = Reduce(intersect, list(top_10_ideators$id,top_10_voters$id))

#Get who are at the top-ten lists of commenters and voters (intersection of two sets)
top_10_comments_votes = Reduce(intersect, list(top_10_commenters$id,
                                               top_10_voters$id))
remove(top_10_m_vc)
for (id in top_10_comments_votes) {
  if (exists("top_10_m_vc")) {
    top_10_m_vc = rbind(top_10_m_vc,c(as.character(top_10_voters[top_10_voters$id==id
                                                                   ,"id"]),
                    paste(top_10_voters[top_10_voters$id==id,"votes"]," (",
                          top_10_voters[top_10_voters$id==id,
                                          "percentage of total"]," of total)", sep=""),
                    paste(top_10_commenters[top_10_commenters$id==id,"comments"],
                          " (",top_10_commenters[top_10_commenters$id==id,
                                                "percentage of total"]," of total)", sep="")))
  } else {
    top_10_m_vc = matrix(c(as.character(top_10_voters[top_10_voters$id==id,"id"]),
                    paste(top_10_voters[top_10_voters$id==id,"votes"]," (",
                          top_10_voters[top_10_voters$id==id,
                                          "percentage of total"]," of total)", sep=""),
                    paste(top_10_commenters[top_10_commenters$id==id,"comments"],
                          " (",top_10_commenters[top_10_commenters$id==id,
                                                "percentage of total"]," of total)", sep="")),
                  ncol=3,byrow=TRUE)      
  }
}
colnames(top_10_m_vc) = c("id","votes","comments")
print(xtable(top_10_m_vc, align=c('c','c','c','c')), type="html", comment=F, include.rownames=F)
#kable(top_10_m_vc,align=c('c','c','c'))
```
